---
title: "Multiple Linear Regression on Customer Data"
author: "Insofe Lab Session"
date: "July 02 , 2017"
output:
  word_document:
    toc_depth: '3'
  pdf_document:
    toc_depth: '3'
  html_document:
    toc_depth: 3
    toc_float: yes
---
```{r}
# Go through the data and understand the attributes to get the info of the variables.
```

Write a code to clear the environment if needed
```{r}
rm(list = ls(all = TRUE))
```

Write a code to set the working directory.
```{r }
setwd("I:/DATA-SCIENCE/Insofe/Assignments/MultipleLinearRegression")

```
Think and load the libraries as and when required in this place only as best practice
```{r}
library(vegan)
library(corrplot)
library(car)
library(DMwR)
library(MASS)
library(e1071)
```
Write a code to read the csv file as "data" as per required
```{r eval=TRUE }
customer.data = read.csv(file = "20170702_Batch30_CSE7302c_CustomerData_Assignment.csv", header = TRUE) 
```
Write a code to know the names of the attributes
```{r}
names(customer.data)
```
Write a code to find the dimensions of the data
```{r}
dim(customer.data)
```

Write a code to see the head  and tail of the dataset atleast 10rows
```{r }
head(x = customer.data, n = 10L)
tail(x = customer.data, n = 10L)
```
Write a code to see the data types of the attributes 
```{r }
str(customer.data)
```
Write a code to remove the unuseful variables and store the data 
```{r }
customer.data.withoutCustomerId = customer.data
customer.data.withoutCustomerId$CustomerID = NULL
```
Write a code to observe the variables and convert them into the required formats
```{r}
summary(customer.data.withoutCustomerId)
# Code to remove the outliers (rows) 
customer.data.withoutCustomerId = customer.data.withoutCustomerId[(customer.data.withoutCustomerId$FrequencyOFPlay < 10000),]
customer.data.withoutCustomerId = customer.data.withoutCustomerId[(customer.data.withoutCustomerId$NoOfChildren <= 10),]
customer.data.withoutCustomerId = customer.data.withoutCustomerId[(customer.data.withoutCustomerId$MinAgeOfChild < 15),]
customer.data.withoutCustomerId = customer.data.withoutCustomerId[customer.data.withoutCustomerId$NoOfGamesBought < 100,]
customer.data.withoutCustomerId = customer.data.withoutCustomerId[customer.data.withoutCustomerId$NoOfGamesPlayed < 500,]
customer.data.withoutCustomerId = customer.data.withoutCustomerId[customer.data.withoutCustomerId$NoOfUnitsPurchased < 50,]
customer.data.withoutCustomerId = customer.data.withoutCustomerId[customer.data.withoutCustomerId$FrquncyOfPurchase < 50,]

#Removing some wrong values in the data and applying KNNImputation to these values
# Age of children can never be greater than 100
customer.data.withoutCustomerId[customer.data.withoutCustomerId$MinAgeOfChild > 100,"MinAgeOfChild"] = NA
customer.data.withoutCustomerId[customer.data.withoutCustomerId$MaxAgeOfChild > 100,"MaxAgeOfChild"] = NA
# Library DMwR
customer.data.withoutCustomerId= knnImputation(data = customer.data.withoutCustomerId, k = 5)

summary(customer.data.withoutCustomerId)

# To convert the vaiables into Factors
categorical.attributes = c("City", "FavoriteChannelOfTransaction", "FavoriteGame")
customer.data.withoutCustomerId[,categorical.attributes] = data.frame(apply(customer.data.withoutCustomerId[,categorical.attributes],2,function(x) as.factor(as.character(x))))
```
Check the changes again using str() command
```{r }
str(customer.data.withoutCustomerId)
```
Write a Code to seperate the target
```{r}
TotalRevenueGenerated = customer.data.withoutCustomerId$TotalRevenueGenerated
```
Write a code to get the numerical attributes out and store them as data_num
```{r }
numerical.attributes = c("NoOfChildren", "MinAgeOfChild", "MaxAgeOfChild", "Tenure", "NoOfUnitsPurchased","FrquncyOfPurchase", "FrequencyOFPlay","NoOfGamesPlayed", "NoOfGamesBought")
data_num = customer.data.withoutCustomerId[, numerical.attributes]
```
Write a code for Normalizing the data_num
```{r}
# Library vegan
normalized.data_num = decostand(data_num, "normalize", MARGIN = 2)
```
Write a code to observe the correlation between the  attributes 
```{r}
r = cor(normalized.data_num)
r
```
Write a code to plot the corrplot of correlation between the attributes
```{r}
# Library corrplot
corrplot(r)
```
Write a code to seperate the categorical attributes
```{r}
data_cat = customer.data.withoutCustomerId[, categorical.attributes]
```
Write a code to combine the numerical,categorical data along with the target 
```{r}
customer.data.withoutCustomerId = cbind(normalized.data_num,data_cat, TotalRevenueGenerated)
```
Write a code to set the seed and comment why it is used.
```{r}
# Setting the seed to make sure that the same set of rows are taken each time when we randomly select the training and test data.
set.seed(1234)
```
Write a code to get the train rows using sample 
```{r}
train.rows = sample(x = 1:nrow(customer.data.withoutCustomerId), size = 0.7*nrow(customer.data.withoutCustomerId))
```
Write a code to get the train and test 
```{r}
# train.data = customer.data.withoutCustomerId[train.rows, ]
# test.data = customer.data.withoutCustomerId[-train.rows, ]
```


```{r}
summary(customer.data.withoutCustomerId)
numeric_Variables = customer.data.withoutCustomerId[,-c(11,12,13)]
target_variable = subset(customer.data.withoutCustomerId,select="TotalRevenueGenerated")
catDummies <- model.matrix(customer.data.withoutCustomerId$TotalRevenueGenerated ~ customer.data.withoutCustomerId$FavoriteChannelOfTransaction + customer.data.withoutCustomerId$FavoriteGame )[,1]

rows=seq(1,nrow(customer.data.withoutCustomerId),1)
set.seed(123)
trainRows=sample(rows,(70*nrow(customer.data.withoutCustomerId))/100)
train1 = data.frame(numeric_Variables, catDummies,TotalRevenueGenerated=target_variable)[trainRows,]
test1 = data.frame(numeric_Variables, catDummies,TotalRevenueGenerated=target_variable)[-trainRows,]

data2 <- as.matrix(data.frame(numeric_Variables, catDummies))
train = data2[trainRows,] 
test = data2[-trainRows,]

#Target Variable
y=customer.data.withoutCustomerId$TotalRevenueGenerated[trainRows]
ytest = customer.data.withoutCustomerId$TotalRevenueGenerated[-trainRows]

library(glmnet)
cv <- cv.glmnet(train,y)  #By default alpha=1
plot(cv)
fit1=glmnet(train,y,lambda=cv$lambda.min,alpha=1)
predict(fit1,train)
library(DMwR)
LASSOtrain = regr.eval(y, predict(fit1,train))
LASSOtest = regr.eval(ytest, predict(fit1,test))
LASSOtrain
LASSOtest


```

Write a code to just plot the grahs between attributes and targets
```{r}
plot(customer.data.withoutCustomerId$City, customer.data.withoutCustomerId$TotalRevenueGenerated)
plot(customer.data.withoutCustomerId$MinAgeOfChild, customer.data.withoutCustomerId$TotalRevenueGenerated)
plot(customer.data.withoutCustomerId$MaxAgeOfChild, customer.data.withoutCustomerId$TotalRevenueGenerated)
plot(customer.data.withoutCustomerId$FrquncyOfPurchase, customer.data.withoutCustomerId$TotalRevenueGenerated)
plot(customer.data.withoutCustomerId$NoOfUnitsPurchased, customer.data.withoutCustomerId$TotalRevenueGenerated)
plot(customer.data.withoutCustomerId$FrequencyOFPlay, customer.data.withoutCustomerId$TotalRevenueGenerated)
plot(customer.data.withoutCustomerId$NoOfGamesPlayed, customer.data.withoutCustomerId$TotalRevenueGenerated)
plot(customer.data.withoutCustomerId$NoOfGamesBought, customer.data.withoutCustomerId$TotalRevenueGenerated)
```
Write a code to form a linear regression model 
```{r}
lm.model.ordinary = lm(TotalRevenueGenerated ~ City + NoOfChildren + MinAgeOfChild + MaxAgeOfChild + NoOfUnitsPurchased + FrquncyOfPurchase + FrequencyOFPlay + (NoOfGamesPlayed * NoOfGamesBought) + FavoriteChannelOfTransaction + FavoriteGame , data = train.data)
```
Write a code to plot the model
```{r}
par(mfrow = c(2,2))
plot(lm.model.ordinary)
```
Write a code to check the summary of the model 
```{r}
summary(lm.model.ordinary)
```
Write a code to predict the value of the target on the linear model 
```{r}
data.predict = predict(lm.model.ordinary, test.data[, !(names(test.data) %in% c("TotalRevenueGenerated"))])


```
Write a code to use stepAIC
```{r}
lm.model.stepAIC = stepAIC(lm.model.ordinary, direction = "both")
```
Write a code to predict it on stepAIC
```{r}
data.predict.stepAIC = predict(lm.model.stepAIC, test.data[, !(names(test.data) %in% c("TotalRevenueGenerated"))])
```
Write a code to check the multicollinearity in the lm model 
```{r}
vif(lm.model.ordinary)
```
Write a code to check the plots of the models
```{r}
par(mfrow = c(2,4))
plot(lm.model.ordinary)
plot(lm.model.stepAIC)
```

Write a code to check the multicollinearity problem
```{r}
vif(lm.model.stepAIC)
```
Write a code to evaluate the error in the prediction of AIC

```{r}
regr.eval(test.data$TotalRevenueGenerated, data.predict.stepAIC)
```
Write a code to evaluate the error on the prediction of Linear Regression
```{r}
regr.eval(test.data$TotalRevenueGenerated, data.predict)
```





